Measuring Interaction Design

### 2015-10-15 paper.tex

  We present a tool (\migtool) that transforms models of a user
  interface into a graph, upon which usage scenarios can be easily
  specified, and used to compute possible interaction paths. Metrics
  based on possible paths, with or without user errors, can be easily
  computed.  For example, when applying them to compare mail
  applications, we show that Gmail has 3 times more shortest routes,
  has 2x more routes that include a single user error, has routes with
  13\% fewer steps, but optimal routes have the smallest probability
  to be chosen.

@@

% REFERENCES FORMAT
% References must be the same font size as other body text.
\bibliographystyle{SIGCHI-Reference-Format}
\bibliography{gb,database}

>>>>

  We present a tool (MIGTool) that transforms models of a user
  interface into a graph, upon which usage scenarios can be easily
  specified, and used to compute possible interaction paths. Metrics
  based on possible paths, with or without user errors, can be easily
  computed.  For example, when applying them to compare mail
  applications, we show that Gmail has 3 times more shortest routes,
  has 2x more routes that include a single user error, has routes with
  13\% fewer steps, but optimal routes have the smallest probability
  to be chosen.

@@

% REFERENCES FORMAT
% References must be the same font size as other body text.
%\bibliographystyle{SIGCHI-Reference-Format}
%\bibliography{gb,database}
%%% -*-BibTeX-*-
%%% Do NOT edit. File created by BibTeX with style
%%% ACM-Reference-Format-Journals [18-Jan-2012].

\begin{thebibliography}{00}

%%% ====================================================================
%%% NOTE TO THE USER: you can override these defaults by providing
%%% customized versions of any of these macros before the \bibliography
%%% command.  Each of them MUST provide its own final punctuation,
%%% except for \shownote{}, \showDOI{}, and \showURL{}.  The latter two
%%% do not use final punctuation, in order to avoid confusing it with
%%% the Web address.
%%%
%%% To suppress output of a particular field, define its macro to expand
%%% to an empty string, or better, \unskip, like this:
%%%
%%% \newcommand{\showDOI}[1]{\unskip}   % LaTeX syntax
%%%
%%% \def \showDOI #1{\unskip}           % plain TeX syntax
%%%
%%% ====================================================================

\ifx \showCODEN    \undefined \def \showCODEN     #1{\unskip}     \fi
\ifx \showDOI      \undefined \def \showDOI       #1{{\tt DOI:}\penalty0{#1}\ }
  \fi
\ifx \showISBNx    \undefined \def \showISBNx     #1{\unskip}     \fi
\ifx \showISBNxiii \undefined \def \showISBNxiii  #1{\unskip}     \fi
\ifx \showISSN     \undefined \def \showISSN      #1{\unskip}     \fi
\ifx \showLCCN     \undefined \def \showLCCN      #1{\unskip}     \fi
\ifx \shownote     \undefined \def \shownote      #1{#1}          \fi
\ifx \showarticletitle \undefined \def \showarticletitle #1{#1}   \fi
\ifx \showURL      \undefined \def \showURL       #1{#1}          \fi

\bibitem{ambler02}
{S. Ambler}. 2002.
\newblock {\em Agile Modeling: Effective Practices for eXtreme Programming and
  the Unified Process}.
\newblock Wiley.
\newblock
\showISBNx{0471202827}

\bibitem{ammann2008introduction}
{P. Ammann} {and} {J. Offutt}. 2008.
\newblock {\em Introduction to software testing}.
\newblock Cambridge University Press.
\newblock

\bibitem{appert2008swingstates}
{C. Appert} {and} {M. Beaudouin-Lafon}. 2008.
\newblock \showarticletitle{SwingStates: adding state machines to Java and the
  Swing toolkit}.
\newblock {\em Software: Practice and Experience\/} {38}, 11 (2008),
  1149--1182.
\newblock

\bibitem{conversy07}
{E. Barboni}, {S. Conversy}, {D. Navarre}, {and} {P. Palanque}. 2007.
\newblock \showarticletitle{Model-based engineering of widgets, user
  applications and servers compliant with ARINC 661 specification}.
\newblock In {\em Interactive Systems. Design, Specification, and
  Verification}. Springer, 25--38.
\newblock

\bibitem{bellamy2011cogtool}
{R. Bellamy}, {B. John}, {and} {S. Kogan}. 2011.
\newblock \showarticletitle{Deploying CogTool: integrating quantitative
  usability assessment into real-world software development}. In {\em Software
  Engineering (ICSE), 2011 33rd International Conference on}. IEEE, 691--700.
\newblock

\bibitem{briand2005:test:uml}
{L.~C Briand}, {Y. Labiche}, {and} {J. Cui}. 2005.
\newblock \showarticletitle{Automated support for deriving test requirements
  from UML statecharts}.
\newblock {\em Software \& Systems Modeling\/} {4}, 4 (2005), 399--423.
\newblock

\bibitem{buxton07}
{B. Buxton}. 2007.
\newblock {\em User Experience: Getting the Design Right and the Right Design}.
\newblock Morgan Kaufmann.
\newblock

\bibitem{ceri:00}
{S. Ceri}, {P. Fraternali}, {and} {A. Bongio}. 2000.
\newblock \showarticletitle{{Web Modeling Language (WebML)}: a modeling
  language for designing web sites}.
\newblock {\em Computer Networks\/}  {33} (2000), 137--157.
\newblock

\bibitem{constantine99}
{L.L. Constantine} {and} {L.A.D. Lockwood}. 1999.
\newblock {\em Software for use: a practical guide to the models and methods of
  usage-centered design}.
\newblock Addison-Wesley.
\newblock

\bibitem{gomez01}
{J. G\'{o}mez}, {C. Cachero}, {and} {O. Pastor}. 2001.
\newblock \showarticletitle{Conceptual Modeling of Device-Independent Web
  Applications}.
\newblock {\em IEEE MultiMedia\/} {8}, 2 (2001), 26--39.
\newblock
\showISSN{1070-986X}
\showDOI{%
\url{http://dx.doi.org/10.1109/93.917969}}

\bibitem{harel09}
{D. Harel}. 2009.
\newblock \showarticletitle{Statecharts in the making: a personal account}.
\newblock {\em CACM\/} {52}, 3 (March 2009), 67--75.
\newblock

\bibitem{heymann2007formal}
{M. Heymann} {and} {A. Degani}. 2007.
\newblock \showarticletitle{Formal analysis and automatic generation of user
  interfaces: approach, methodology, and an algorithm}.
\newblock {\em Human Factors: The Journal of the Human Factors and Ergonomics
  Society\/} {49}, 2 (2007), 311--330.
\newblock

\bibitem{hilbert2000}
{D.~M Hilbert} {and} {D.F. Redmiles}. 2000.
\newblock \showarticletitle{Extracting usability information from user
  interface events}.
\newblock {\em ACM Computing Surveys (CSUR)\/} {32}, 4 (2000), 384--421.
\newblock

\bibitem{hornbaek2006current}
{K. Hornb{\ae}k}. 2006.
\newblock \showarticletitle{Current practice in measuring usability: Challenges
  to usability studies and research}.
\newblock {\em International Journal of Human-Computer Studies\/} {64}, 2
  (2006), 79--102.
\newblock

\bibitem{horrocks99}
{Ian Horrocks}. 1999.
\newblock {\em Constructing the User Interface with Statecharts}.
\newblock Addison-Wesley Longman Publishing Co., Inc., Boston, MA, USA.
\newblock
\showISBNx{0201342782}

\bibitem{john04cogtool}
{B.E. John}, {K. Prevas}, {D.D. Salvucci}, {and} {K. Koedinger}. 2004.
\newblock \showarticletitle{Predictive human performance modeling made easy}.
  In {\em Proc. of the Int. Conf. on Human Factors in Computing Systems}. ACM,
  New York, NY, USA, 455--462.
\newblock

\bibitem{koch02:uwe}
{N. Koch} {and} {A. Kraus}. 2002.
\newblock \showarticletitle{{The expressive power of {UML}-based web
  engineering}}. In {\em Second International Workshop on Web-Oriented Software
  Technology (IWWOST02)}, {D.~Schwabe}, {O.~Pastor}, {G.~Rossi}, {and}
  {L.~Olsina} (Eds.). 105--199.
\newblock

\bibitem{mccurdy06}
{M. McCurdy}, {C. Connors}, {G. Pyrzak}, {B. Kanefsky}, {and} {A. Vera}. 2006.
\newblock \showarticletitle{Breaking the fidelity barrier: an examination of
  our current characterization of prototypes and an example of a mixed-fidelity
  success}. In {\em CHI 2006}. ACM, ACM Press, New York, NY, 1233--1242.
\newblock

\bibitem{melia08}
{S. Meli\'a}, {J. G\'omez}, {S. P\'erez}, {and} {O. D\'iaz}. 2008.
\newblock \showarticletitle{A Model-Driven Development for GWT- Based Rich
  Internet Applications with OOH4RIA}. In {\em Proc. 8th Int'l Conf. Web Eng.
  (ICWE 2008)}. IEEE CS Press, 13--23.
\newblock

\bibitem{mori02}
{G. Mori}, {F. Patern\`o}, {and} {C. Santoro}. 2002.
\newblock \showarticletitle{{CTTE: Support for Developing and Analysing Task
  Models for Interactive System Design}}.
\newblock {\em IEEE Transactions on Software Engineering\/} {28}, 8 (August
  2002), 797--813.
\newblock

\bibitem{ifml13}
{{OMG}}. 2013.
\newblock {\em Interaction Flow Modeling Language ({IFML}), FTF -- Beta 1\/}
  (omg document number: ptc/2013-03-08 ed.).
\newblock {T}echnical {R}eport. OMG.
\newblock
\showURL{%
\url{http://www.omg.org/spec/IFML/1.0}}

\bibitem{uml25}
{{Object Management Group} OMG}. 2015.
\newblock {OMG Unified Modeling Language ({OMG UML})} Version 2.5.
\newblock \url{http://www.omg.org/spec/UML/2.5}.   (March 2015).
\newblock
\showURL{%
\url{http://www.omg.org/spec/UML/2.5/PDF}}

\bibitem{otter2000lostness}
{M. Otter} {and} {H. Johnson}. 2000.
\newblock \showarticletitle{Lost in hyperspace: metrics and mental models}.
\newblock {\em Interacting with Computers\/} {13}, 1 (2000), 1--40.
\newblock

\bibitem{page1999pagerank}
{L. Page}, {S. Brin}, {R. Motwani}, {and} {T. Winograd}. 1999.
\newblock \showarticletitle{The PageRank citation ranking: bringing order to
  the Web.}
\newblock  (1999).
\newblock

\bibitem{parnas69}
{D.L. Parnas}. 1969.
\newblock \showarticletitle{On the use of transition diagrams in the design of
  a user interface for an interactive computer system}. In {\em ACM '69 Proc.
  of the 1969 24th National Conference}. ACM.
\newblock

\bibitem{silva03:umli}
{P. Pinhero~da Silva} {and} {N.W. Paton}. 2003.
\newblock \showarticletitle{User Interface Modeling in {UMLi}}.
\newblock {\em IEEE Software\/} (2003), 62--69.
\newblock

\bibitem{preece02}
{J. Preece}, {Y. Rogers}, {and} {H. Sharp}. 2002.
\newblock {\em Interaction design}.
\newblock John Wiley and Sons.
\newblock

\bibitem{rubin08}
{J. Rubin} {and} {D. Chisnell}. 2008.
\newblock {\em Handbook of Usability Testing\/} (second ed.).
\newblock Wiley.
\newblock

\bibitem{samek09}
{M. Samek}. 2009.
\newblock {\em Practical {UML} Statecharts in {C/C++}}.
\newblock Elsevier.
\newblock

\bibitem{smith1996lostness}
{P.A. Smith}. 1996.
\newblock \showarticletitle{Towards a practical measure of hypertext
  usability}.
\newblock {\em Interacting with Computers\/} {8}, 4 (1996), 365--381.
\newblock

\bibitem{thimbleby07}
{H. Thimbleby}. 2007.
\newblock {\em Press on: principles of interaction programming}.
\newblock The MIT Press.
\newblock

\bibitem{thimbleby2001markov}
{H. Thimbleby}, {P. Cairns}, {and} {M. Jones}. 2001.
\newblock \showarticletitle{Usability analysis with Markov models}.
\newblock {\em ACM Transactions on Computer-Human Interaction (TOCHI)\/} {8}, 2
  (2001), 99--132.
\newblock

\bibitem{thimbleby09:sna:eics09}
{H. Thimbleby} {and} {P. Oladimeji}. 2009.
\newblock \showarticletitle{Social Network Analysis and Interactive Device
  Design Analysis}. In {\em Proc. of Engineering Interactive Computing Systems
  2009}. ACM Press, 91--100.
\newblock

\end{thebibliography}
